---
output:
  md_document
---

### Age, rent, and green buildings

The first question to address is whether green buildings are actually newer, on average.

```{r}
library(tidyverse)
greenbuildings = read.csv('../../data/greenbuildings.csv')
ggplot(greenbuildings) + 
  geom_point(aes(x=age, y=Rent))
```


The next questio nis whether building age is systematically different between green and non-green buildings.  In the plot below, we see clearly that they are:
```{r}
ggplot(greenbuildings) + 
  geom_histogram(aes(x=age, y=stat(density)), binwidth=2) + 
  facet_grid(green_rating~.)
```

Notice here we can see the whole distribution of ages by green status, and we recognize the second group of older non-green buildings that is largely missing among the green-rated buildings.  


<!-- # The truly excellent answer: try to hold age roughly constant -->

<!-- # easy way: -->
<!-- # define some age groupings -->
<!-- greenbuildings = mutate(greenbuildings,  -->
<!--                         agecat= cut(age, c(0, 10, 20, 30, 50, 75, 200), include.lowest =TRUE)) -->

<!-- # now compare rent within age groupings -->
<!-- summ1 = greenbuildings %>% -->
<!--   group_by(agecat, green_rating) %>% -->
<!--   summarize(mean_rent = mean(Rent), n = n()) -->
<!-- summ1 -->

<!-- summ1 %>% select(agecat, green_rating, mean_rent) %>% -->
<!--   spread(green_rating, mean_rent) -->

<!-- # in bar plot form -->
<!-- ggplot(summ1) +  -->
<!--   geom_col(aes(x=agecat, y=mean_rent, fill=factor(green_rating)), position='dodge') -->

<!-- # Note: comparison is much easier within categories this way, versus stacked bars! -->
<!-- ggplot(summ1) +  -->
<!--   geom_col(aes(x=agecat, y=mean_rent, fill=factor(green_rating)), position='stack') -->

